Writing Trash Bin

### 2024-08-02 paper.qmd
BIG edit (I forgot to commit). Finished visualising uncertainty as a variable *and* the EDA issue with VSUP

<!-- TODO 
- convert to American spelling
- May not need to reference the same paper again and again
- examples that aren't maps? Sure are a lot of maps.
-->

@@

## Why this approach may (or may not) work
Unfortunately it is not enough to only understand the purpose of uncertainty visualisation. To do signal-suppression successfully we need to understand what uncertainty actually *is*, as this will inform us on how it should be integrated into the visualisaiton.

### It's a variable... it's a metadata... it's uncertainty?
Describing what uncertainty *is* is actually suprisingly hard. Most authors simply avoid the problem and describe the characteristics of uncertainty, of which there are plenty. Often, uncertainty is split using an endless stream of ever changing boundaries, such as whether the uncertainty is due to true randomness or a lack of knowledge [@Spiegelhalter2017; @Hullman2016; @utypo], if the uncertainty is in the attribute, spatial elements, or temporal element of the data [@Kinkeldey2014], whether the uncertainty is scientific (e.g. error) or human (e.g. disagreement among parties) [@Benjamin2018], if the uncertainty is random or systematic [@Sanyal2009], statistical or bounded [@Gschwandtnei2016; @Olston2002], recorded as accuracy or precision [@Griethe2006; @Benjamin2018], which stage of the data analysis pipeline the uncertainty comes from [@utypo], how quantifiable the uncertainty is [@Spiegelhalter2017; @utypo], etc.

There are enough qualitative descriptors of uncertainty to fill a paper, but, none of this is particularly helpful in understanding how to integrate it into a visualisation. Rather than trying to define uncertainty by what it *is* it may be easier to try and describe what uncertainty *is not*. Thankfully, the literature on what uncertainty is *not* is much more specific.

Descriptive statistics describe our sample as it is and summarizes large data down into an easy to swallow format. Descriptive statistics are not seen as the primary goal of modern statistics, however, this was not always the case. In 19th century England, *positivism* was the popular philosophical approach to science (positivists included famous statisticians such as Francis Galton and Karl Pearson). Practitioners of the approach believed statistics ended with descriptive statistics as science must be based on actual experience and observations [@Otsuka2023]. In order to make statements about population statistics, future values, or new observations we need to perform inference, which requires the assumption of the "uniformity of nature", i.e. we need to assume that unobserved phenomena should be similar to observed phenomena [@Otsuka2023]. Positivists abore the assumption of the "uniformity of nature" as they believed that reference to the unobservable is not true science. In other words, these scientists embraces descriptive statistics and shunned inferential statistics due to the fact inferential statistics introduces uncertainty.

This history lesson illustrates what uncertainty actually is. A by-product of inference. This means that anything that could lead us to violate our uniformity of nature assumption, is a source of uncertainty. The qualitative characteristics of uncertainty provided by our taxonomies all highlight aspect

feared 
This subtle shift, from descriptive statistics to inferential statistics was shunned during the positivism era *due to the fact it introduced the unknowable*, or in other words, uncertainty. 
While we may agree on the *purpose* of uncertainty, it is an entirely different can of worms to agree on what uncertainty actually *is*. @fig-bivariate uses variance as a proxy for uncertainty, however those terms are not perfect synonyms.

### Visualising the "single integrated uncertain value"
Uncertainty visualisation is a uniquely difficult problem. @Hullman2016 commented that it is straightforward to show a value but it is much more complex to show uncertainty. This difficulty is often described as a high-dimensional visualisation problem, as the difficulty in uncertainty visualisation is in working out how to add uncertainty into already existing graphics [@moritz2017trust; @Griethe2006]. The problem with this approach to uncertainty visualisation is that it treats uncertainty the same as we would any other variable, but we are not interested in visualising uncertainty as though it were any other variable.

Typically, when making visualisations, we want the visual channels to be separable, that is, we don't want the data represented through one visual channel to interfere with the others [@Smart2019]. This is not the goal of uncertainty visualisation. The goal of uncertainty visualisations is to display signal and uncertainty together as a "single integrated uncertain value" [@Kinkeldey2014].  Separability allows for the signal and the uncertainty to be read separately which allows for the uncertainty information to simply be ignored when reading the signal, which is a pervasive issue in current uncertainty visualisation methods [@uncertchap2022]. We can see this problem in @fig-bivariate, as it sends the message "this data has a spatial trend and the estimates have a large variance" as we read the signal and the uncertainty separately.

The need for interference from the uncertainty channel does not necessarily mean high-dimensional visualisation techniques would be useless for uncertainty visualisation. High-dimensional visualisation methods could work if the uncertainty and the estimates were mapped to integrable channels. That is, the visual channels would need to be separately manipulable, but read as a single channel by the human brain. While most visual aesthetics *are* separable, there are some variables that have been shown to be integrable, such as color hue and brightness [@Vanderplas2020]. When visualising uncertainty using its own visual channel, we can also consider visual semiotics and make sure to map uncertainty to intuitive visual channels, such as mapping more uncertain values to lighter colors [@Maceachren2012].

@@

@fig-vsup is a visualisation of the Iowa temperature data using a VSUP to color the counties. The low uncertainty case still has a visible spatial trend, while the spatial trend in the high uncertainty map has functionally disappeared. This means the VSUP has successfully performed signal suppression for our data.

@@

Now that we have successfully suppressed our invalid signal, we must return to the original criteria we had for signal supression and ask ourselves if we meet all of them. We want to make sure that in our efforts to suppress invalid signals, we have not also suppressed statistically *valid* signals in the process.

## Can we have uncertinty visualisations for EDA?
A slight problem with uncertainty visualisation is that the uncertainty and the purpose of visualisation are somewhat at odds with one another. The VSUP highlights this problem quite well.

There are two primary motivations behind visualisation, communication and exploratory data analysis (EDA). Communication involves identifying a signal we want to communicate and designing a visualisation that best conveys that, while EDA involves creating a versatile visualisation using it to extract several signals. It is not uncommon for authors to express a desire for uncertainty visualisations that perform signal-suppression in visualisations made for EDA [@Sarma2024; @Griethe2006], however it is not clear that these uncertainty visualisations *exist at all*.

The impossible task of making this graphic is easy to see with a simple example. Let's say we have a graphic that depicts a set of coefficients from a linear regression and the value of the coefficient is shown using a single colour. We do a series of t-tests on these estimates, and all of them fail to reject the null hypothesis that they are different from 0. This would indicate that each value needs to be visualised using a single color that is indistinguishable from the colour assigned to 0. However, we also perform an f-test on our model, and this test *is* rejected. This test indicates that the set of estimates should not be visually indistinguishable from 0. This is clearly a contradiction.

This t-test, f-test example highlights a fundamental problem with the VSUP and even the bivariate map. When we blend colors to make them visually indistinguishable, we need to decide at what level of *uncertainty* to blend these colors together. There is no intrinsic mapping of uncertainty, so we need to make a decision as to how much signal-suppression the visualisation should perform. There is no existing rule or accepted practice in how to go about this, but it is present in every uncertainty graphic. Even though the bivariate map was not explicitly combining temperature values at certain variance levels, the mapping of variance to color saturation does this implicitly. That is, at certain saturation values the colors in a bivariate map are imperceptibly different and appear as though they are mapped to the same value, regardless of whether or not that is actually the case.

Regardless as to whether the map colors are implicitly or explicitly indistinguishable, the point at which the colors blend together can only be validated by a single hypothesis. Therefore, using the methods discussed thus far, it would be impossible to design signal-suppression for EDA. If we are designing a graphic for communication then we can suppress the signal we were seeking to communicate, but this would rely on the distinction between EDA and communication to be somewhat clear cut. Visualization authors may design a graphic with a particular purpose, but what the visualization *is actually* used for is determined by the viewer and some authors have discussed the validity of there being any distinction between visualisation motivation's at all [@Hullman2021]. However, this problem only exists when we color each cell using a single color. If we can color a cell using multiple colors, this limitation may disappear entirely.

@@

## What even is "uncertainty" anyway?
The pixel map is not the best uncertainty visualisation, but it is trying to *replicate* the best uncertainty visualisation. The best uncertainty visualisation is the visualisation that best captures the limitations of of our raw data.

## variance is not uncertainty
This approach to uncertainty is embedded in the idea that descriptive statistics do not have uncertainty, which some readers may disagree with. Specifically, because it means uncertainty is *not* a latent attribute of data, but rather an attribute of a specific hypothesis or estimate. Deniers of this fact follow a consistent logical path and it is easy to identify the common mistake. We know that variance and probability are typically considered types of "uncertainty" *and* descriptive statistics can have variance and probabilities *therefore* descriptive statistics must have uncertainty. The flaw in this logic comes from the first step, assuming that the tools with which we measure uncertainty *are* uncertainty in of themselves. This confusion is common and there are many papers that spend a great deal of time clarifying the difference. @Begg2014 highlight that uncertainty is related to not knowing a specific value, while variability refers to the range of values a quantity can take at different locations, times or instances. @Spiegelhalter2017 made sure to comment on the difference between precise random events (such as the probability associated with a coin flip), and uncertainty (such as the estimated probability associated with a coin that might be biased). The variance of a sample variance can be calculated and know, therefore it is not uncertain but rather it a precise description of dispersion. If we were to discuss drawing a new observation, or estimating the true mean of a population *then* the variance would become relevant in our discussions of uncertainty.

@@

@@

### Problems with uncertainty having no definition
The ramifications of this problem is seen repeatedly in the uncertainty visualisation literature. A survey of visualisation authors cited "not knowing how to calculate uncertainty" as one of the primary reasons they did not include it in visualisations [@Hullman2020a]. Some works [@Hullman2018; @Maceachren2012; @Thomson2005] ignore the problem get around this definition issue by focusing narrowly on specific terms defined mathematically, such as probability, variance, error, or precision. Others [@Griethe2006; @Pang1997; @Pham2009; @Boukhelifa2017] include broader loosely related elements, such as missing values, but ignore these concepts when translating that uncertainty to a visualisation. Existing mathematical definition of uncertainty (or related concepts) have been unable to unify this range of diverse concepts. For example, @Thomson2005 suggests a mathematical formula for *examples* of uncertainty, and information theory tries to quantify uncertainty using the idea of entropy, but the disconnect between the broad concept of uncertainty and what we can reliably quantify remains a problem.

@@

### EDA is descriptive statistics
 Since EDA is the visual parallel to descriptive statistics, it is performed without an explicit hypothesis which means there *is* no uncertainty in the visualisation. Similarly to our issues with descritive statistics, this is not well understood by the uncertainty visualisation community. Some authors simply confuse varianc for uncertainty. For example @Potter2010 aimed to create a summary plot that "concisely presented data with uncertainty information" to create an exploratory visualisation tool that visualised uncertainty. Other authors regonise inference will occur (in some shape or form) and believe uncertainty *should* be visualised but do not recognise *how* uncertainty would be visualised. @Hullman2021 argued that there is no such thing as a "model-free" visualisation, therefore visualisation require robust visualisations of uncertainty as we are always performing inference.  @Griethe2006 commented that "if visualization is used as a means to explore a data volume or to communicate its contents the uncertainty has to be included". While we agree people cannot prevent themselves from performing inference, that does not mean it is possible for uncertainty to be included in an EDA visualisation. A versatile visualisation such as a scatter plot allows for a viewer to consider several hypothesis at once, each of which will be a different inferential statistic with a different distribution that depicts its uncertainty. It is likely impossible to suppress all possible signals at once.

@@

### Just noticeable signal
It could be argued that a well done uncertainty visualisations should have an imperceptible signal unless the signal would be identified with a hypothesis test, almost like a reverse line up protocol, but this idea also has some issues that should be considered. The reject or do not reject concepts in hypothesis testing do not offer a complete image of uncertainty, and exploration of uncertainty visualisation largely stems from a desire to move away from this binary framework.

>>>>

<!-- TODO 
- convert to American spelling
- May not need to reference the same paper again and again
  - I am not sure when I need a citation and when I dont. Sometimes I could literally cite hundreds of papers to make a point, so I'm not sure if i should cite any at all.
- examples that aren't maps? Sure are a lot of maps.
-->

@@

## Why this approach may (or may not) work
The difficulty in incorporating uncertainty into a visualisation is frequently mentioned but seldom explained. For example @Hullman2016 commented that it is straightforward to show a value but it is much more complex to show uncertainty but did not explain why. Many authors seem to believe uncertainty visualisation is a simple high-dimensional visualisation problem, as the difficulty comes from working out how to add uncertainty into already existing graphics [@moritz2017trust; @Griethe2006]. The problem with this approach to uncertainty visualisation is that it treats uncertainty the same as we would any other variable. However, @fig-bivariate makes it clear that simply including uncertainty as a variable is insufficient to perform signal-suppresion. If we cannot treat uncertainty as any other variable, what should we treat it as? We need to understand what uncertainty actually *is*, in order to understand how to integrate it into a visualisation.

### It's a variable... it's a metadata... it's uncertainty?
Describing what uncertainty actually is, is surprisingly hard. Most authors simply avoid the problem and describe the characteristics of uncertainty, of which there are plenty. Often, uncertainty is split using an endless stream of ever changing boundaries, such as whether the uncertainty is due to true randomness or a lack of knowledge [@Spiegelhalter2017; @Hullman2016; @utypo], if the uncertainty is in the attribute, spatial elements, or temporal element of the data [@Kinkeldey2014], whether the uncertainty is scientific (e.g. error) or human (e.g. disagreement among parties) [@Benjamin2018], if the uncertainty is random or systematic [@Sanyal2009], statistical or bounded [@Gschwandtnei2016; @Olston2002], recorded as accuracy or precision [@Griethe2006; @Benjamin2018], which stage of the data analysis pipeline the uncertainty comes from [@utypo], how quantifiable the uncertainty is [@Spiegelhalter2017; @utypo], etc. There are enough qualitative descriptors of uncertainty to fill a paper, but, none of this is particularly helpful in understanding how to integrate it into a visualisation.

Rather than trying to define uncertainty by what it *is* it may be easier to try and describe what uncertainty *is not*. Descriptive statistics describe our sample as it is and summarizes large data down into an easy to swallow format. Descriptive statistics are not seen as the primary goal of modern statistics, however, this was not always the case. In 19th century England, *positivism* was the popular philosophical approach to science (positivists included famous statisticians such as Francis Galton and Karl Pearson). Practitioners of the approach believed statistics ended with descriptive statistics as science must be based on actual experience and observations [@Otsuka2023]. In order to make statements about population statistics, future values, or new observations we need to perform inference, which requires the assumption of the "uniformity of nature", i.e. we need to assume that unobserved phenomena should be similar to observed phenomena [@Otsuka2023]. Positivists abhore the assumption of the "uniformity of nature" as they believed referencing the unobservable is bad science. In other words, these scientists embraces descriptive statistics and shunned inferential statistics due to the inherent uncertainty that came with them. Uncertainty is a by-product of inference.

This history lesson illustrates what uncertainty actually is. At several stages in a statistical analysis, we will violate the "uniformity of nature" assumption. Each of these violations will impact the statistic we have calculated and push it further from the population parameter we wish to draw inference on. Uncertainty is the amalgamation of these impacts. If we do not violate the uniformity of nature assumption at any point in our analysis, we do not have any uncertainty.

This interpretation of uncertainty indicates that the uncertainty on a statistic is not of value in of itself. Uncertainty is metadata about our statistic that is required for valid inference. This means uncertainty should not be visualised by itself and we should seek to display signal and uncertainty together as a "single integrated uncertain value" [@Kinkeldey2014]. This aspect of uncertainty visualization makes it a uniquely difficult problem. This is something frequently mentioned

### Visualising the "single integrated uncertain value"
Typically, when making visualisations, we want the visual channels to be separable, that is, we don't want the data represented through one visual channel to interfere with the others [@Smart2019]. Mapping uncertainty and signal to separable channels allows them to be read separately, which does not align with the goal of communicating them as a "single integrated channel". Additionally, visualizing uncertainty and signal separately allows the uncertainty information to simply be ignored, which is a pervasive issue in current uncertainty visualisation methods [@uncertchap2022]. We can see this problem in @fig-bivariate, as it sends the message "this data has a spatial trend and the estimates have a large variance" as we read the signal and the uncertainty separately.

This means effective uncertainty visualisation should be leveraging integrability. That is, the visual channels of the uncertainty and the signal would need to be separately manipulable, but read as a single channel by the human brain. While most visual aesthetics *are* separable, there are some variables that have been shown to be integrable, such as color hue and brightness [@Vanderplas2020]. When visualizing uncertainty using its own visual channel, we can also consider visual semiotics and make sure to map uncertainty to intuitive visual channels, such as mapping more uncertain values to lighter colors [@Maceachren2012].

@@

@fig-vsup is a visualisation of the Iowa temperature data using a VSUP to color the counties. The low uncertainty case still has a visible spatial trend, while the spatial trend in the high uncertainty map has functionally disappeared. This means the VSUP has successfully suppressed the spatial trend in the data. However the spatial trend may not be the only signal of concern in our graphic. Now we must return to the original signal-suppression criteria and ask ourselves if they have all been met. Are all the justified signals reinforced, while all the unjustified signals are suppressed? Is a graphic that performs perfect signal-suppression even possible?

@@

## What can and cannot be suppressed?
The methods used by the VSUP bring to light a slight problem with uncertainty visualisation. Specifically that uncertainty and the purpose of visualisation are somewhat at odds with one another. There are two primary motivations behind visualisation, communication and exploratory data analysis (EDA). Communication involves identifying a signal we want to communicate and designing a visualisation that best conveys that, while EDA involves creating a versatile visualisation using it to extract several signals. If we are designing an uncertainty visualisation for communication then we can just suppress the specific signal we are seeking to communicate. In the map example, we would consider @fig-vsup to be a success as the only signal we are concerned with is the spatial trend. However, it is not uncommon for authors to express a desire for uncertainty visualisations that perform signal-suppression in visualisations made for EDA [@Sarma2024; @Griethe2006]. Unfortunately it is not clear whether or not uncertainty visualisations for EDA are possible.

### There is no uncertainty in EDA
Earlier we established that uncertainty is a by-product of inference, which means without inference, there is no uncertainty. Often EDA is used to give us an understanding of our data and identify which signals are worth pursuing. In this sense, EDA is the visual parallel to descriptive statistics, as it is performed without an explicit hypothesis which means there is no inference, and by extension, there is no uncertainty.

Some authors recognize inference will occur (in some shape or form) and believe uncertainty *should* be visualised but do not recognize *how* uncertainty would be visualised. @Hullman2021 argued that there is no such thing as a "model-free" visualisation, therefore all visualisations require uncertainty as we are always performing inference. While we agree that people cannot prevent themselves from performing inference, this does not mean it is possible to include uncertainty in a visualisation designed for EDA. However, this does mean we should endeavor for a versatile uncertainty visualisation method that is able to perform signal-suppression on all the signals displayed in the visualisation. It is unlikely that the methods discussed thus far are able to achieve this.

### The limitations of explicitly visualising uncertainty and signal
The lack of versatility of the VSUP is easy to see with a simple example. Let's say we have a graphic that depicts a set of coefficients from a linear regression and the value of the coefficient is shown using a single color. We want to know "Which of these coefficients are different from 0?" as well as "Which of these coefficients are different from each other?". To answer this question we do a series of t-tests on these estimates.

All of the individual t-tests of fail to reject the null hypothesis that the coefficients are different from 0. We then make a visualisation that suppresses this signal and ensures that all of the estimates are visually indistinguishable from 0. We then do a comparison of two means t-test and find that several of the values need to be visually distinguishable from each other. The VSUP method must pick a single color for each estimate, and these colours must be *either* visually distinguishable or indistinguishable from each other. We cannot perform signal-suppression on both these signals simultaneously.

This example highlights a fundamental problem with the VSUP that extends to the bivariate map as well. When we blend these colors, we need to decide at what level of *uncertainty* to blend these colors together. Even though the bivariate map does not explicitly combine color values at certain variance levels, the mapping of variance to color saturation does this implicitly. That is, at certain saturation values the colors in a bivariate map are imperceptibly different to the human brain and appear as though they are mapped to the same value. At this point, it is irrelevant whether or not the colours are technically different, they are the same color in the human brain.  Which hypothesis are suppressed and which are not largely depends on the method used to combining colors in the palette [@Kay2019]. The VSUP here used a tree based method as that is what was used by @Correll2018, but there are alternatives that are more appropriate for different hypothesis.

If we only use a single value to express each signal-suppressed statistic, we will always need to decide which signals we suppress and which we do not. However, If we could express the statistic of a cell using multiple colors, this limitation may disappear entirely.

@@

## Where is all this uncertainty coming from?
The pixel map is not the best uncertainty visualisation, but it is trying to *replicate* the best uncertainty visualisation. The best uncertainty visualisation is the visualisation that best captures the limitations of of our raw data.

### variance is not uncertainty
This approach to uncertainty is embedded in the idea that descriptive statistics do not have uncertainty, which some readers may disagree with. Specifically, because it means uncertainty is *not* a latent attribute of data, but rather an attribute of a specific hypothesis or estimate. Deniers of this fact follow a consistent logical path and it is easy to identify the common mistake. We know that variance and probability are typically considered types of "uncertainty" *and* descriptive statistics can have variance and probabilities *therefore* descriptive statistics must have uncertainty. The flaw in this logic comes from the first step, assuming that the tools with which we measure uncertainty *are* uncertainty in of themselves. This confusion is common and there are many papers that spend a great deal of time clarifying the difference. @Begg2014 highlight that uncertainty is related to not knowing a specific value, while variability refers to the range of values a quantity can take at different locations, times or instances. @Spiegelhalter2017 made sure to comment on the difference between precise random events (such as the probability associated with a coin flip), and uncertainty (such as the estimated probability associated with a coin that might be biased). The variance of a sample variance can be calculated and know, therefore it is not uncertain but rather it a precise description of dispersion. If we were to discuss drawing a new observation, or estimating the true mean of a population *then* the variance would become relevant in our discussions of uncertainty.

@@

Some authors simply confuse variance for uncertainty. For example @Potter2010 aimed to create a summary plot that "concisely presented data with uncertainty information" to create an exploratory visualisation tool that visualised uncertainty.

@@

### Problems with uncertainty having no definition
The ramifications of this problem is seen repeatedly in the uncertainty visualisation literature. A survey of visualisation authors cited "not knowing how to calculate uncertainty" as one of the primary reasons they did not include it in visualisations [@Hullman2020a].

Unfortunately "the amalgamations of the impacts of violations to the assumption of the uniformity of nature" is a rather broad concept that does not easily roll off the tongue. Regardless, this definition of uncertainty does seem to align with what the literature considers to be included in the uncertainty umbrella. Some works [@Hullman2018; @Maceachren2012; @Thomson2005] focus narrowly on specific terms with mathematical definitions, such as probability, confidence intervals, variance, error, or precision. These works are only concerned with quantifying the final impact of uncertainty on our statistics. That is, how large should the bound around our statistic be, such that our "true" statistic can be inferred. Others [@Griethe2006; @Leland2005; @Pang1997; @Pham2009; @Boukhelifa2017] include broader loosely related elements, such as missing values, reliability, model validity, or source integrity. These broader and harder to quantify concepts are concerned about potential sources of uncertainty, that is, they describe violations to the assumption of the uniformity of nature.

Existing mathematical definition of uncertainty (or related concepts) have been unable to unify this range of diverse concepts. For example, @Thomson2005 suggests a mathematical formula for *examples* of uncertainty, and information theory tries to quantify uncertainty using the idea of entropy, but the disconnect between the broad concept of uncertainty and what we can reliably quantify remains a problem.

@@

@@

### Just noticeable signal

there are some papers that do identify signal suppress effects, but they discuss it as a failure rather than a success.

It could be argued that a well done uncertainty visualisations should have an imperceptible signal unless the signal would be identified with a hypothesis test, almost like a reverse line up protocol, but this idea also has some issues that should be considered. The reject or do not reject concepts in hypothesis testing do not offer a complete image of uncertainty, and exploration of uncertainty visualisation largely stems from a desire to move away from this binary framework.

### 2024-08-02 writingdumpster.qmd
BIG edit (I forgot to commit). Finished visualising uncertainty as a variable *and* the EDA issue with VSUP

# Removed Sections
After all, if we consider a choropleth map, which ignores uncertainty entirely to be at one end of the spectrum (it is a map that only cares about showing signals reguardless of whether or not they are valid) then a completely colourless map is at the other end of the spectrum (it is a map that only cares about suppressing signals regardless of whether or not they are valid).

@@

>>>>

# Removed Sections
@Griethe2006 commented that "if visualization is used as a means to explore a data volume or to communicate its contents the uncertainty has to be included".

After all, if we consider a choropleth map, which ignores uncertainty entirely to be at one end of the spectrum (it is a map that only cares about showing signals reguardless of whether or not they are valid) then a completely colourless map is at the other end of the spectrum (it is a map that only cares about suppressing signals regardless of whether or not they are valid).

@@

# Data description
Consider our Iowa temperature map, let $X$ be the 12pm temperature taken within each county on for each day in May from 2000 to 2024. Unfortunately, we are given a data set that does not include $X$, instead we have the average of $X$, $\hat{X_k}$ and the variance of $X$, $\hat{VarX}$ for each county, $\forall k=1,...,n$ where $n$ is the total number of counties. Theoretically, the estimate and its variance should provide enough information for us to

# EDA
Regardless as to whether the map colors are implicitly or explicitly indistinguishable, the point at which the colors blend together can only be validated by a single hypothesis. Therefore, using the methods discussed thus far, it would be impossible to design signal-suppression for EDA. If we are designing a graphic for communication then we can suppress the signal we were seeking to communicate, but this would rely on the distinction between EDA and communication to be somewhat clear cut. Visualization authors may design a graphic with a particular purpose, but what the visualization *is actually* used for is determined by the viewer and some authors have discussed the validity of there being any distinction between visualisation motivation's at all [@Hullman2021].

# Bivariate map saturation mapping
Since changes in the color value and hue can also cause the colors to blend together, the mapping of uncertainty to saturation would also affect the signal-suppression in these maps. To correctly map uncertainty, we would need to be able to answer how many units of saturation a 1 unit change in variance worth? There are no existing guidelines, but similar to the suppression method, the choice in colour mapping would depend on the signals we hope to suppress.
